Security Metrics for the Android Ecosystem

### 2015-07-27 dastats.tex
Use Spearmans Rank rather than Damerau-Levenshtein distance

\newcommand{\daTabSpearmanRanks}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & summary \\ $\pm\sigma$ & 0.211 & 0.169 & 0.175 & 0.632 \\ \hline $u$ & 0.297 & 0.804 & 0.618 & 1.0 \\$m$ & 0.794 & 0.593 & 0.969 & -1.0 \\$f$ & 0.83 & 0.775 & 0.934 & 1.0 \\weight $u$ & 0.939 & 0.996 & 0.991 & 1.0 \\weight $m$ & 0.976 & 0.964 & 0.996 & 1.0 \\equal & 1.0 & 0.996 & 1.0 & 1.0 \\\end{tabular} \caption{Spearman Rank correlation coefficients for different metrics} \label{tab:dl_distances} \end{table}}

>>>>

\newcommand{\daTabSpearmanRanks}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & summary \\ $\pm\sigma$ & 0.211 & 0.169 & 0.175 & 0.632 \\ \hline $u$ & 0.297 & 0.804 & 0.618 & 1.0 \\$m$ & 0.794 & 0.593 & 0.969 & -1.0 \\$f$ & 0.83 & 0.775 & 0.934 & 1.0 \\weight $u$ & 0.939 & 0.996 & 0.991 & 1.0 \\weight $m$ & 0.976 & 0.964 & 0.996 & 1.0 \\equal & 1.0 & 0.996 & 1.0 & 1.0 \\\end{tabular} \caption{Spearman Rank correlation coefficients for different metrics. The uncertainty is constant for each column but does not take into account the uncertainty in the score which produced the ranking.} \label{tab:spearman_ranks} \end{table}}

### 2015-07-27 security_scoring.tex
Use Spearmans Rank rather than Damerau-Levenshtein distance

\subsection{Sensitivity of scoring metric}
\daTabDLDistances
\daTabChangeInScores
To evaluate whether the ranking of different manufacturers is sensitive to the form of the scoring metric we computed the normalised Damerau-Levenshtein distance~\cite{Bard2007} between the lists ordered using different forms of the scoring metric, this is shown in Table~\ref{tab:dl_distances}.
The `equal' metric weights $f$, $u$ and $m$ equally rather than favouring $f$ and makes little difference.
Changing the scoring metric also impacts the scores given for each entity Table~\ref{tab:change_in_scores} shows the mean impact on the scores.
This shows that $m$ tends to drag down scores.
\todolater{Give some of the actual orderings as well for the most important ones - no space}
\todolater{Sensitivity of time based vs. global scores}
\todo{Reviewer 3 thinks we should use the Spearman rank correlation coefficient instead, and they might be right, currently being computed}

>>>>

\subsection{Sensitivity of scoring metric}
\daTabSpearmanRanks
\daTabChangeInScores
To evaluate whether the ranking of different manufacturers is sensitive to the form of the scoring metric we computed the normalised Spearman's Rank correlation coefficient between the lists ordered using different forms of the scoring metric, this is shown in Table~\ref{tab:spearman_ranks}.
The `equal' metric weights $f$, $u$ and $m$ equally rather than favouring $f$ and makes little difference.
Similarly weighting $u$ or $m$ more highly rather than $f$ makes little difference.
While the $f$, $u$ and $m$ components do have some correlation with the overall FUM score, the rankings produced vary substantially.
Changing the scoring metric also impacts the scores given for each entity Table~\ref{tab:change_in_scores} shows the mean impact on the scores.
This shows that $m$ tends to drag down scores.
\todolater{Give some of the actual orderings as well for the most important ones - no space}
\todolater{Sensitivity of time based vs. global scores - no time}
